---
title: "Data & Method"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

------------------------------------------------------------------------

# Data

<br>

In the present study, data will be webscraped from the internet to
answer the research question. The study will focus on scientists working
at the Sociology department and scientists working at the Data Science
department of Radboud University. Information on publications,
co-authorship and citations will be scraped from Google Scholar using
the Scholar package in R. Social media participation will be expressed
using the Kardashian Index, which compares the Twitter followers with
number of citations of academics (Hall, 2014). In order to calculate
these, the twitteR package in R will be used to extract Twitter user
information of scholars of the departments. Using the number of
followers and the citations, the index can be calculated. Data will be
collected for two different times, and then the evolution of the
networks of Sociology and Data Science will be compared.

Summarized, it can be expressed as follows:

**Nodes** The scientists of both departments mentioned (thus focusing on
the micro-level)

**Edges** Co-authorship between these scientists (yes/no)

**Dependent variable** Not exactly sure yet. Density of the network.
Homophily? But I don't have everyone's research interests.

**Independent variable** Kardashian Index of the scientists. To measure
the influence effects, a model will be analyzed including the Kardashian
Index as a dependent variable.

**Control variables** Gender and age.

<br>

# Method

In order to study the networks, the RSiena package will be used. SIENA
is able to analyze longitudinal data simulating network outcomes based
on the perspective of the nodes (Ripley, Snijders, Boda, Voros &
Preciado, 2022) TO WHAT EXTENT DO I EXPLAIN THIS? First, the evaluation
effects will be studied, which focuses on which ties are present.

<br> 

# References 

Hall, N. (2014). The Kardashian index: A measure of
discrepant social media profile for scientists. Genome Biology, 15(7),
424. <https://doi.org/10.1186/s13059-014-0424-0>

Ruth M. Ripley, Tom A.B. Snijders, Zs ́ofia Boda, Andr ́as V ̈or ̈os,
and Paulina Preciado, 2022. Manual for SIENA version 4.0 (version August
11, 2022). Oxford: University of Oxford, Department of Statistics;
Nuffield College.
