---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Hypotheses

Also descriptive hypotheses? For which people I expect a higher
Kardashian Index (not really related to networks)

*Scientists, because of the homophily effect, like to select scientist
that are rather similar in their KI.*

Scientists with a high Kardashian Index more popular: Hall explains that
sometimes scientific speakers are invited because of their popularity,
not based on good publications --\> maybe now social media has become
more popular, scientists indeed attach value to other scientists,
regardless of whether they have good publications or not. Thus then
scientists with a high KI could still be popular. *Scientists prefer to
co-publish with other scientists that have a high KI*

Question: Should I also run a model where I disregard the Kardashian
Index but only look at Twitter follower count?

On the other hand, maybe scientists with a high KI are very unpopular
because they are criticized for being active on social media but not
really contributing to science. If this is true, then the following
hypothesis can be expected: *Scientists prefer to co-publish with other
scientist that have a low KI*.
