---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

The rise of the Internet, like on many aspects in life, has had an
influence on social networks (Licoppe & Smoreda, 2005). Because o the
internet, selection and influence processes have changed. Literature on
mate-selection shows that when using the Internet to find a partner,
individuals tend to select partners that show more similarity when
compared to couples that selected each other in offline settings (Carter
& Buckwalter, 2009). Also, within online friendship relations, a high
level of homophily is visible (Aiello et al., 2012).

However, less is known about the influence of social media on networks
of scientists. On the one hand, following the literature on mate- and
friendship selection, it is interesting to investigate whether
scientists select other scientists that are similarly active on social
media. On the other hand, it is possible that scientists with social
media popularity will also become attractive to be selected by others to
collaborate. In the current paper, I would like to investigate several
research questions to gain more insights into the influence of social
media on networks of scientists at two academic departments: *How do
scientists within the Sociology and Data Science department of Radboud
University differ in social media activity?* And, *how do scientists
between the Sociology and Data Science department of Radboud University
differ in social media activity?*

While these questions are descriptive in nature, I would also like to
investigate network effects. For this, the Kardashian Index (Hall, 2014)
will be used. This index expresses the ratio between scientists'
popularity on social media and their publishing of significant
peer-reviewed papers. A high Kardashian Index means that a scientist may
be 'overvalued', while a low Kardashian Index means an undervaluation of
a scientist. To study the possible influence of the Kardashian Index on
a network based on co-publication, I aim to answer the following
research question: *To what extent does the Kardashian Index influence
network dynamics of co-publication networks of the Sociology and Data
Science department at Radboud University?*

NEED TO ADJUST THIS PART 

An answer to this question is both relevant to society and to science.
The evolution of social networks is not only relevant to the individuals
within that network, but is also a signifier of cohesion (SOURCE) and
inequality (Karimi et al., 2018). Since individuals are embedded in
networks, the decisions these individuals make within these networks
will also affect the societal level (EXPLAIN MORE CLEARLY). In this
case, investigating how social media participation has an influence on
selecting collaborators within one network of scientists, could be
translated into the influence of social media on networks in general.
Possibly, selection mechanisms have changed as a consequence of social
media and therefore it has an influence on cohesion. The current paper
will also add to the literature by applying a social network
perspective. Performing a social network analysis is of added value, as
it can reveal precisely how selection in social networks may alter as a
consequence of social media. This reveals to a deeper extent which
mechanisms underlie the influence of internet on cohesion.
