---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Data & Methods

## Dependent variable

In the present study, I webscraped data from the internet in order to
answer the research questions. The study focuses on scientists working
at the Sociology department (N=33) and scientists working at the Data
Science department (N=46) of Radboud University. The starting point of
the webscraping was collecting the full names of these scientists from
the staff-webpage of the Radboud University. In order to do so, I used
the package rvest was, and in case of JavaScript data, the package V8 to
gather this information.

In the next step, these full names were used by the Scholar package in R
to find information on publications, co-authorship and citations. I
deleted scientists with an extremely high number of citations, which
resulted in deleting three scientists at the Sociology department and
two at the Data Science department. With this data, I created the
dependent variable co-publications. For each scientist, I searched
whether this scientist had published an article with someone else from
the same department. This was done using the names of the scientists.
Although this data was collected at one moment in time, with the
publication network I had the opportunity to distinguish different
moments in time. Per department, there are three waves of co-publication
networks: for the years 2016-2017, 2018-2019 and 2020-2022. These waves
thus express the co-publication ties of articles published in these
years. I then turned these three waves into an adjacency matrix, in
which scientists score a 1 when they have published an article together.
Since the network is based on co-publications, it is undirected.

## Independent variable

The independent variable consists of the Kardashian Index. The
Kardashian Index compares the Twitter followers with number of citations
of academics [@hall_kardashian_2014]. In order to calculate these, the
twitteR package in R is used to extract Twitter user information of
scholars of the departments from the Twitter REST API. For each full
name, the first user that the twitteR package scraped, is saved. By
eyeballing, twitter users with a high number of followers were checked.
In some cases, the match between full name and Twitter username was not
made correctly. In those instances, this was corrected by hand. Using
the number of followers and the citations scraped from Google Scholar,
the Kardashian Index is calculated. Hall's [-@hall_kardashian_2014]
formula to calculate the k-index exists of two equations. The first
equation calculates a typical number of twitter followers and is
expressed as follows:



$$ F = 43.3C^{0.32} $$

Then, the k-index is calculated with the following equation, using the actual followercount and the expected followercount: 

$$ K-index = \frac{F_{a}} {F_{c}} $$

<br>

## Control variables

I added the control variable Twitter Dummy to indicate whether the
scientist has Twitter or not. A scientist scores 1 in case of a Twitter
handle found by the twitteR package. Furthermore, the variable Dutch
shows the ethnicity of the scientist. This variable is included as a
selection to collaborate with a scientist may also be based on their
ethnicity. Ethnicity was scraped using the Familienamenbank
[@nederlandse_familienamenbank], which has data on last names used in
the Netherlands. In case of a typical Dutch last name, the scientist got
a score 1 on the dummy Dutch. In other cases, the scholar scores a 0.
This means that all last names that are not Dutch are taken together as
one category, not distinguishing between (Non-)Western ethnic
backgrounds.

As gender may influence the k-index as well as collaborations between
scientists, I included a dummy for gender. With a procedure similar to
that of determining ethnicity, the Meertens namenbank
[@databanken_meertens_instituut] was used to determine the gender of the
respondent. This databank has information on all the first names used in
the Netherlands and their frequency. In case of a first name that is
more often used for women than for men, a scientist scores a 0 on the
dummy gender. In case of a first name that is more often used for men,
the scientist scores a 1 on the dummy. Lastly, as age can have an
influence on opportunities for (co)publishing, a proxy for age is
included based on the year of the first publication of the scholar. The
descriptives of these variables can be found at the bottom of this page.

Interested readers may have a further look into the scraping of all the
variables used during this study, which can be done with the replication
package that can be found on this website in week 3 of the "My Journal"
page.

<br>

# Analytical strategy

To answer the research questions that are descriptive in nature,
descriptive statistics are shown for the different waves and different
study departments. These statistics are then used to compare within and
between departments and to answer the research questions. Important
descriptive network characteristics that I show are transitivity, degree
and the dyad census.

To provide an answer to the explanatory research question on network
effects, the RSiena package is used. SIENA -- which stands for
Simulation Investigation for Empirical Network Analysis -- is able to
analyze longitudinal data simulating network outcomes based on the
perspective of the nodes [@manual]. Importantly, the Stochastic Actor
Oriented Model (SOAM) entails that actors perform 'ministeps', which
means that a random actor gets assigned at the time, who is able to make
one tie change. After making this tie change, the next actor gets the
turn to make a change. For these actors, it is also a possibility to
make no change. The decision of the actor depends on the evaluation of
possible options, which is determined with the evaluation function. The
actor then bases the decision on the most attractive network outcome.
After this decision, the next actor gets a turn to decide. Based on many
simulations of these actor-decisions, estimates for evaluation are
provided by the model.

## Estimation of models

Three models are estimated per department. In the first model, only
structural network effects on the dependent variable of co-publication
are included. First, the *degree* effect estimates the number of
outdegrees, which are in this case the number of copublications. This
effect can be interpreted as an intercept. Then, the *transitive triads*
effect shows whether individuals prefer to close a triad (and thus
prefer a transitive relation) than to not close a transitive triad. In
the case of co-publication networks, it means whether a scientist
prefers to co-publish with a co-author of a co-author. Furthermore, the
activity and popularity effect reveals whether individuals prefer to
form a tie with individuals that already have a lot of ties. Thus, do
scientists co-publish with scientists that have already co-published a
lot?

In the second model, the k-index is added. In this model, the *absDiffX*
effect was included, estimating whether scientists prefer to co-publish
with a scientist with a low absolute discrepancy in their k-index. I
thus used this effect to test the homophily based on the k-index. Then
another model is run with the control variables included. For the
control variables ethnicity, gender and the Twitter dummy, I included
the *sameX* effect. This shows whether scientists prefer to co-publish
with another scientist of the same gender, ethnicity and twitter status.
As age is the only control variable of ratio measurement level, I
included this variable with the *absDiffX* effect as well, as I would
like to see whether scientists prefer to collaborate with someone
similar in age, not of exactly the same age.

In the fourth model, the *altX* effect was included for the k-index, to
test the hypotheses on co-publishing with scientists with a lower or
higher k-index. This effect shows whether scientists prefer to
co-publish based on the value of the k-index of the other scientist. The
last model tests these *altX* effects with control variables included.
All of the control variables included in the model remain the same as in
the third model.

As robustness checks, the same models as described above were estimated
without the twitter dummy, and with the number of twitter followers as
independent variable instead of the k-index. This could show whether it
may mostly be social media that matters without its relation to the
citations of a scientist. These robustness checks are visible in the
Appendix.

```{r}
load("/Users/anuschka/Documents/labjournal/data/socdef_df.RData")
summary(socdef_df$ki)
summary(socdef_df$dutch)
summary(socdef_df$pub_first)
summary(socdef_df$twitter_dum)
table(socdef_df$gender)

```

```{r}
load("/Users/anuschka/Documents/labjournal/data/datadef_df.RData")
summary(datadef_df$ki)
summary(datadef_df$dutch)
summary(datadef_df$pub_first)
summary(datadef_df$twitter_dum)
table(datadef_df$gender)

```

# References
