---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Theory

## Collaboration networks of scientists

Scientific collaboration networks have been studied more often within
social network analysis, as they are an example of a constantly changing
network [@barabasi_evolution_2002]. These studies have shown that
scientific collaboration networks can often be described as highly
clustered [@newman_structure_2001], with scientists collaborating more
often when they have a third common scientist as compared to two random
scientists collaborating. Barabasi et al.
[-@barabasi_evolution_2002]also conclude that these scientific
collaboration networks are often marked by preferential attachment,
meaning in this case that scientists with many collaboration ties get
even more ties. Furthermore, homophily is also present within networks
of scientific collaboration, showing that scientists have a preference
of working together with scientists of the same institution or with
similar research interests [@wang_homophily_2014].

These network structures that are typical for scientific collaboration
networks are thus important to consider, and provide the opportunity to
test the effects of several characteristics of scientists while also
taking into account the consequences these network effects bring about.
The effect of high clustering that Newman [-@newman_structure_2001]
described, is also called "transitivity". This describes the tendency
among individuals to form a tie with another individual who already has
a tie with someone known (e.g. becoming friends with friends of friends)
[@block_reciprocity_2015]. Scientists thus prefer to collaborate with
scientists that have collaborated with one of my collaborators.

While the literature on (network effects within) scientific
collaboration networks may be well-established
[@barabasi_evolution_2002; @block_reciprocity_2015;
@newman_structure_2001; @wang_homophily_2014 ], less is known about
other factors that could have an effect of selection and influence in
networks. While transitivity, homophily and preferential attachment
provide clear expectations as to which scientist collaborates with whom
and why, other elements could also determine collaborations between
scientists. In this study, the influence of Twitter activity and its
relation to popularity of scientific publications is investigated for
co-publication networks of scientists.

## Kardashian Index and expectations

Hall [-@hall_kardashian_2014] developed the Kardashian Index to quantify
whether social media use of scientists is becoming more important than
scientific output. This k-index is a ratio between the number of Twitter
followers of a scientist and the number of citations for scientific
articles. According to Hall [-@hall_kardashian_2014], scientists with a
k-index higher than 5, are strongly overvalued and have built their
public profile based on social media while not having highly cited
articles.

The k-index is more often used within the literature. For instance,
Kolahi and colleagues [-@kolahi_analysis_2019] found that scientific
dental articles that covered important topics, were often not among the
highly tweeted articles. On the other hand, they also found that the
highly tweeted articles had 12.96 cites on average, possibly
demonstrating a correlation between number of tweets and citations.
While Kohali and colleagues [-@kolahi_analysis_2019] focused mostly on
articles as subject of their research, Khan and colleagues
[-@khan2020kardashian] investigated the k-index of cardiologists among a
random sample drawn from cardiologists of the top 100 hospitals and
found that the majority of the cardiologists had a rather low k-index,
and that only some ranked above the number of 5.

Most of the literature using the k-index is descriptive in nature and
does not look at any influences on and consequences of the k-index.
Eacott [-@eacott_educational_2020] did investigate the k-index and the
Twitter tagging relations of scientists and concluded that scientists
who get mentioned a lot are not necessarily of scientific value. What
remains unclear, is whether this k-index also has an influence on social
networks of scientists. As scientists that are popular on social media
now get invited to speak at events because of their popularity
[@hall_kardashian_2014] and not because of highly cited publications,
this may signal that scientists attach value to other scientists that
have a strong social media outreach. In this context, the citations of a
scientists may be of less importance, making scientists with a high
k-index attractive for other scientists to collaborate. Therefore, I
derive the first hypothesis: *Scientists prefer to co-publish with other
scientists that have a high k-index.*

On the other hand, scientists are in general critical individuals. This
may result in unpopularity of scientists with a high k-index, as they
could be known for investing more time in social media than in
contributing to science [@califf_perspective_2020]. This leads to the
second hypothesis: *Scientists prefer to co-publish with other
scientists that have a low k-index.*

Furthermore, as explained above, the homophily effect is important
within social networks [@wang_homophily_2014]. Possibly, not only the
research topics of other scientists are taken into consideration when
selecting others to co-publish with, but also a similar stance regarding
the ratio between social media and scientific contributions. Thus, the
scientist compares their own k-index with that of another scientist. In
this regard, it can be expected that scientists select other scientists
with a similar k-index for co-publication. Therefore, the last
hypothesis can be derived as follows: *Scientists prefer to co-publish
with other scientists that have a similar k-index.*

# References
