---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Introduction

The rise of the Internet, like on many aspects in life, has had an
influence on social networks [@licoppe_are_2005]. Because of the
internet, selection and influence processes have changed. Literature on
mate-selection shows that when using the Internet to find a partner,
individuals tend to select partners that show more similarity when
compared to couples that selected each other in offline settings [@carter_enhancing_2009]. Also, within online friendship relations, a high
level of homophily is visible [@aiello_friendship_2012].

However, less is known about the influence of social media on
collaboration networks of scientists. While the collaboration networks
of scientists are studied more often [@barabasi_evolution_2002], the
role of social media remains unclear. The current study therefore delves
deeper into this role of social media on offline social networks. More
specifically, I will not only consider the social media activity, but
also its relation to total scientific citations. For this, the
Kardashian Index(k-index) [@hall_kardashian_2014] will be used. This index
expresses the ratio between scientists' popularity on Twitter and their
publishing of significant peer-reviewed papers. A high k-index means
that a scientist may be 'overvalued', while a low k-index means an
undervaluation of a scientist.

Investigating the k-index is especially relevant in the context of
collaborations of scientists, as it could reveal whether scientists
attach more or less value to online "performance" of co-authors than to
actual scientific performance. If it is the case that scientists with a
high k-index are more popular to be selected for collaboration, this may
indicate that there is a shift in focus within academia from scientific
production towards importance online [@califf_perspective_2020]. It is questionable
whether this is a desirable development, especially if this will be at
the cost of doing good research [@eacott_educational_2020]. Furthermore, even if
this k-index is not of value, this could indicate that scientists are
not critical on co-publishing with over- or undervalued scientists.
These insights in possibly altering influence processes for choosing
scientific collaborators are also relevant more generally, as it could
signal a discrepancy between individuals' online and offline status, in
which online status could become more important.

Following the literature on online mate- and friendship selection
[@carter_enhancing_2009], it is on the one hand interesting to
investigate whether scientists select other scientists that are
similarly active on social media. On the other hand, it is possible that
scientists with social media popularity will also become attractive to
be selected by others to collaborate (Hall, 2014). As no literature yet
is able to describe the directions of these influences, in the current
paper, I would like to investigate several research questions to gain
more insights into the influence of the Kardashian Index on networks of
scientists at two academic departments: *How do scientists within the
Sociology and Data Science department of Radboud University differ in
their Kardashian Index?* And; *How do scientists between the Sociology
and Data Science department of Radboud University differ in their
Kardashian Index?*

While these questions are descriptive in nature, I would also like to
investigate network effects. To study the possible influence of the
Kardashian Index on a network based on co-publications, I aim to answer
the following research question: *To what extent does the Kardashian
Index influence network dynamics of co-publication networks of the
Sociology and Data Science department at Radboud University?* The latter
question is answered using the Stochastic Actor-Orientated Modelling
(SOAM) of RSiena [@manual], which enables me to investigate
the effect of the Kardashian Index on collaboration, while controlling
for structural network effects and other characteristics that are of
influence on collaboration.

The scientific contribution of this study is thus twofold: First, it
adds to the gap in the literature on the influence of social media
within collaboration networks of scientists. Second, this is not only
done descriptively, but also by performing a SOAM-analysis, taking into
account structural network effects. While for instance regression
analyses could test which individual characteristics are related to a
scientist's k-index, the current study also looks at whether this
k-index influences decisions a scientist makes in their selection of
co-authors, and whether this holds when taking into account the
structure of the network the scientist is embedded in. This will be
investigated by webscraping data on the two departments at Radboud
University.

# References

