---
title: "introduction"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

------------------------------------------------------------------------

# Introduction

I could not spend as much time on it as I wished, so this weekend I'll
have time to improve the introduction.

The rise of the Internet, like on many aspects in life, has had an
influence on social networks (Licoppe & Smoreda, 2005). Especially
social media has altered networks, as it provides opportunities to
activate latent ties and strengthen weak ties (Haythornthwaite, 2002);
more recent source). Furthermore, the selection and influence within
networks has changed. Literature on mate-selection shows that when using
the Internet to find a partner, individuals tend to select partners that
show more similarity when compared to couples that selected each other
in offline settings (Carter & Buckwalter, 2009). Also within online
friendship relations, a high level of homophily is visible (Aiello et
al., 2012).

However, less is known about the influence of social media on networks
of scientists. Increased opportunities to communicate online may have
created new collaborations between co-authors. It is interesting to
investigate whether these collaborations show a high level of homophily
as we would expect following the literature on mate- and friendship
selection. Simultaneously, these novel options to find co-authors
online, may have resulted in a less dense network as a result of often
selecting new co-authors to collaborate with. This may create
differences in network structure between scientists that are active
online and scientists who are not. In the current paper, I would like to
investigate the following research question: How does being active on
social media impact collaborations in social networks of scientists?

An answer to this question is both relevant to society and to science.
The evolution of social networks is not only relevant to the individuals
within that network, but is also a signifier of cohesion (SOURCE) and
inequality (Karimi et al., 2018). Since individuals are embedded in
networks, the decisions these individuals make within these networks
will also affect the societal level (EXPLAIN MORE CLEARLY). In this
case, investigating how social media participation has an influence on
selecting collaborators within one network of scientists, could be
translated into the influence of social media on networks in general.
Possibly, selection mechanisms have changed as a consequence of social
media and therefore it has an influence on cohesion. The current paper
will also add to the literature by applying a social network
perspective. Performing a social network analysis is of added value, as
it can reveal precisely how selection in social networks may alter as a
consequence of social media. This reveals to a deeper extent which
mechanisms underlie the influence of internet on cohesion.

# References

Aiello, L. M., Barrat, A., Schifanella, R., Cattuto, C., Markines, B., &
Menczer, F. (2012). Friendship prediction and homophily in social media.
ACM Transactions on the Web, 6(2), 9:1-9:33.
<https://doi.org/10.1145/2180861.2180866> Carter, S. R., & Buckwalter,
J. G. (2009). Enhancing Mate Selection through the Internet: A
Comparison of Relationship Quality between Marriages arising from an
Online Matchmaking System and Marriages arising from Unfettered
Selection. Interpersona: An International Journal on Personal
Relationships, Extra 3, 105--125. Hall, N. (2014). The Kardashian index:
A measure of discrepant social media profile for scientists. Genome
Biology, 15(7), 424. <https://doi.org/10.1186/s13059-014-0424-0>
Haythornthwaite, C. (2002). Strong, Weak, and Latent Ties and the Impact
of New Media. The Information Society, 18(5), 385--401.
<https://doi.org/10.1080/01972240290108195> Karimi, F., Génois,
M.,Wagner, C., Singer, P., & Strohmaier, M. (2018). Homophily influences
ranking of minorities in social networks. Scientific Reports, 8(1),
11077. <https://doi.org/10.1038/s41598-018-29405-7> Licoppe, C.,
&Smoreda, Z. (2005). Are social networks technologically embedded?: How
networks are changing today with changes in communication technology.
Social Networks, 27(4), 317--335.
<https://doi.org/10.1016/j.socnet.2004.11.001>
