---
title: "Tutorial R Siena"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---

```{r warning=FALSE, globalsettings, echo=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r, eval=FALSE}
rm(list=ls())
```

# RSiena tutorial

```{r, eval=FALSE}
#install.packages("RSiena")
library(RSiena)
friend.data.w1 <- s501
friend.data.w2 <- s502
friend.data.w3 <- s503
drink <- s50a
smoke <- s50s
friendship <- sienaDependent(array(c(friend.data.w1, friend.data.w2, friend.data.w3), dim = c(50, 50,
    3)))
smoke1 <- coCovar(smoke[, 1])
alcohol <- varCovar(drink)
mydata <- sienaDataCreate(friendship, smoke1, alcohol)
# and request
mydata
# to see what you have produced.
```


```{r, eval=FALSE}
myalgorithm <- sienaAlgorithmCreate(projname = NULL)
```

```{r, eval=FALSE}
myeff <- getEffects(mydata)
myeff <- includeEffects(myeff, transTrip, cycle3)
myeff <- includeEffects(myeff, egoX, altX, egoXaltX, interaction1 = "alcohol")
myeff <- includeEffects(myeff, simX, interaction1 = "smoke1")
myeff
```
```{r, eval=FALSE}
ans <- siena07(myalgorithm, data = mydata, effects = myeff)
summary(ans)
```


```{r, eval=FALSE}
myeff <- setEffect(myeff, inPopSqrt, fix = TRUE, test = TRUE, initialValue = 0)
ans <- siena07(myalgorithm, data = mydata, effects = myeff, prevAns=ans)
summary(ans)
```


# Twitter manual 
```{r, eval=FALSE}
# density: observed relations divided by possible relations
fdensity <- function(x) {
    # x is your nomination network make sure diagonal cells are NA
    diag(x) <- NA
    # take care of RSiena structural zeros, set as missing.
    x[x == 10] <- NA
    sum(x == 1, na.rm = T)/(sum(x == 1 | x == 0, na.rm = T))
}

# calculate intragroup density
fdensityintra <- function(x, A) {
    # A is matrix indicating whether nodes in dyad have same node attributes
    diag(x) <- NA
    x[x == 10] <- NA
    diag(A) <- NA
    sum(x == 1 & A == 1, na.rm = T)/(sum((x == 1 | x == 0) & A == 1, na.rm = T))
}

# calculate intragroup density
fdensityinter <- function(x, A) {
    # A is matrix indicating whether nodes in dyad have same node attributes
    diag(x) <- NA
    x[x == 10] <- NA
    diag(A) <- NA
    sum(x == 1 & A != 1, na.rm = T)/(sum((x == 1 | x == 0) & A != 1, na.rm = T))
}

# construct dyadcharacteristic whether nodes are similar/homogenous
fhomomat <- function(x) {
    # x is a vector of node-covariate
    xmat <- matrix(x, nrow = length(x), ncol = length(x))
    xmatt <- t(xmat)
    xhomo <- xmat == xmatt
    return(xhomo)
}

# a function to calculate all valid dyads.
fndyads <- function(x) {
    diag(x) <- NA
    x[x == 10] <- NA
    (sum((x == 1 | x == 0), na.rm = T))
}

# a function to calculate all valid intragroupdyads.
fndyads2 <- function(x, A) {
    diag(x) <- NA
    x[x == 10] <- NA
    diag(A) <- NA
    (sum((x == 1 | x == 0) & A == 1, na.rm = T))
}


fscolnet <- function(network, ccovar) {
    # Calculate coleman on network level:
    # https://reader.elsevier.com/reader/sd/pii/S0378873314000239?token=A42F99FF6E2B750436DD2CB0DB7B1F41BDEC16052A45683C02644DAF88215A3379636B2AA197B65941D6373E9E2EE413
    
    fhomomat <- function(x) {
        xmat <- matrix(x, nrow = length(x), ncol = length(x))
        xmatt <- t(xmat)
        xhomo <- xmat == xmatt
        return(xhomo)
    }
    
    fsumintra <- function(x, A) {
        # A is matrix indicating whether nodes constituting dyad have same characteristics
        diag(x) <- NA
        x[x == 10] <- NA
        diag(A) <- NA
        sum(x == 1 & A == 1, na.rm = T)
    }
    
    # expecation w*=sum_g sum_i (ni((ng-1)/(N-1)))
    network[network == 10] <- NA
    ni <- rowSums(network, na.rm = T)
    ng <- NA
    for (i in 1:length(ccovar)) {
        ng[i] <- table(ccovar)[rownames(table(ccovar)) == ccovar[i]]
    }
    N <- length(ccovar)
    wexp <- sum(ni * ((ng - 1)/(N - 1)), na.rm = T)
    
    # wgg1 how many intragroup ties
    w <- fsumintra(network, fhomomat(ccovar))
    
    Scol_net <- ifelse(w >= wexp, (w - wexp)/(sum(ni, na.rm = T) - wexp), (w - wexp)/wexp)
    return(Scol_net)
}
```


```{r, eval=FALSE}
getwd()
load("/Users/anuschka/Documents/labjournal/data/twitter_20190919.RData")  #change to your working directory
```


```{r, eval=FALSE}
str(twitter_20190919, 1)
keyf <- twitter_20190919[[1]]
mydata <- twitter_20190919[[2]]
seats <- twitter_20190919[[3]]
```

```{r, eval=FALSE}
# retrieve nominationdata from rsiena object
fnet <- mydata$depvars$fnet
atmnet <- mydata$depvars$atmnet
rtnet <- mydata$depvars$rtnet

# retrieve node-attributes from rsiena object
vrouw <- mydata$cCovars$vrouw
partij <- mydata$cCovars$partij
ethminz <- mydata$cCovars$ethminz
lft <- mydata$cCovars$lft

# de-mean-center node attributes
ethminz <- ethminz + attributes(ethminz)$mean
partij <- partij + attributes(partij)$mean
vrouw <- vrouw + attributes(vrouw)$mean
lft <- lft + attributes(lft)$mean

# construct matrices for similarity for each dimension (dyad characteristics)
vrouwm <- fhomomat(vrouw)
partijm <- fhomomat(partij)
ethminzm <- fhomomat(ethminz)

# just for fun, make dyad characteristic indicating whether both nodes are ethnic minorities
xmat <- matrix(ethminz, nrow = length(ethminz), ncol = length(ethminz))
xmatt <- t(xmat)
minoritym <- xmat == 1 & xmatt == 1

# for age max 5 year difference / for descriptives
xmat <- matrix(lft, nrow = length(lft), ncol = length(lft))
xmatt <- t(xmat)
lftm <- (abs(xmat - xmatt) < 6)

# calculate all possible similar dyads, not the focus of this exercise.  fndyads2(fnet[,,1], vrouwm)
# fndyads2(fnet[,,3], vrouwm) fndyads2(fnet[,,1], partijm) fndyads2(fnet[,,3], partijm)
# fndyads2(fnet[,,1], ethminzm) fndyads2(fnet[,,3], ethminzm)

# make a big object to store all results
desmat <- matrix(NA, nrow = 10, ncol = 9)

# lets start using our functions
desmat[1, 1] <- fdensity(fnet[, , 1])
desmat[1, 2] <- fdensity(fnet[, , 2])
desmat[1, 3] <- fdensity(fnet[, , 3])
desmat[2, 1] <- fdensityintra(fnet[, , 1], vrouwm)
desmat[2, 2] <- fdensityintra(fnet[, , 2], vrouwm)
desmat[2, 3] <- fdensityintra(fnet[, , 3], vrouwm)
desmat[3, 1] <- fdensityinter(fnet[, , 1], vrouwm)
desmat[3, 2] <- fdensityinter(fnet[, , 2], vrouwm)
desmat[3, 3] <- fdensityinter(fnet[, , 3], vrouwm)
desmat[4, 1] <- fdensityintra(fnet[, , 1], partijm)
desmat[4, 2] <- fdensityintra(fnet[, , 2], partijm)
desmat[4, 3] <- fdensityintra(fnet[, , 3], partijm)
desmat[5, 1] <- fdensityinter(fnet[, , 1], partijm)
desmat[5, 2] <- fdensityinter(fnet[, , 2], partijm)
desmat[5, 3] <- fdensityinter(fnet[, , 3], partijm)
desmat[6, 1] <- fdensityintra(fnet[, , 1], ethminzm)
desmat[6, 2] <- fdensityintra(fnet[, , 2], ethminzm)
desmat[6, 3] <- fdensityintra(fnet[, , 3], ethminzm)
desmat[7, 1] <- fdensityinter(fnet[, , 1], ethminzm)
desmat[7, 2] <- fdensityinter(fnet[, , 2], ethminzm)
desmat[7, 3] <- fdensityinter(fnet[, , 3], ethminzm)
desmat[8, 1] <- fdensityinter(fnet[, , 1], minoritym)
desmat[8, 2] <- fdensityinter(fnet[, , 2], minoritym)
desmat[8, 3] <- fdensityinter(fnet[, , 3], minoritym)
desmat[9, 1] <- fdensityintra(fnet[, , 1], lftm)
desmat[9, 2] <- fdensityintra(fnet[, , 2], lftm)
desmat[9, 3] <- fdensityintra(fnet[, , 3], lftm)
desmat[10, 1] <- fdensityinter(fnet[, , 1], lftm)
desmat[10, 2] <- fdensityinter(fnet[, , 2], lftm)
desmat[10, 3] <- fdensityinter(fnet[, , 3], lftm)

desmat[1, 1 + 3] <- fdensity(atmnet[, , 1])
desmat[1, 2 + 3] <- fdensity(atmnet[, , 2])
desmat[1, 3 + 3] <- fdensity(atmnet[, , 3])
desmat[2, 1 + 3] <- fdensityintra(atmnet[, , 1], vrouwm)
desmat[2, 2 + 3] <- fdensityintra(atmnet[, , 2], vrouwm)
desmat[2, 3 + 3] <- fdensityintra(atmnet[, , 3], vrouwm)
desmat[3, 1 + 3] <- fdensityinter(atmnet[, , 1], vrouwm)
desmat[3, 2 + 3] <- fdensityinter(atmnet[, , 2], vrouwm)
desmat[3, 3 + 3] <- fdensityinter(atmnet[, , 3], vrouwm)
desmat[4, 1 + 3] <- fdensityintra(atmnet[, , 1], partijm)
desmat[4, 2 + 3] <- fdensityintra(atmnet[, , 2], partijm)
desmat[4, 3 + 3] <- fdensityintra(atmnet[, , 3], partijm)
desmat[5, 1 + 3] <- fdensityinter(atmnet[, , 1], partijm)
desmat[5, 2 + 3] <- fdensityinter(atmnet[, , 2], partijm)
desmat[5, 3 + 3] <- fdensityinter(atmnet[, , 3], partijm)
desmat[6, 1 + 3] <- fdensityintra(atmnet[, , 1], ethminzm)
desmat[6, 2 + 3] <- fdensityintra(atmnet[, , 2], ethminzm)
desmat[6, 3 + 3] <- fdensityintra(atmnet[, , 3], ethminzm)
desmat[7, 1 + 3] <- fdensityinter(atmnet[, , 1], ethminzm)
desmat[7, 2 + 3] <- fdensityinter(atmnet[, , 2], ethminzm)
desmat[7, 3 + 3] <- fdensityinter(atmnet[, , 3], ethminzm)
desmat[8, 1 + 3] <- fdensityinter(atmnet[, , 1], minoritym)
desmat[8, 2 + 3] <- fdensityinter(atmnet[, , 2], minoritym)
desmat[8, 3 + 3] <- fdensityinter(atmnet[, , 3], minoritym)
desmat[9, 1 + 3] <- fdensityintra(atmnet[, , 1], lftm)
desmat[9, 2 + 3] <- fdensityintra(atmnet[, , 2], lftm)
desmat[9, 3 + 3] <- fdensityintra(atmnet[, , 3], lftm)
desmat[10, 1 + 3] <- fdensityinter(atmnet[, , 1], lftm)
desmat[10, 2 + 3] <- fdensityinter(atmnet[, , 2], lftm)
desmat[10, 3 + 3] <- fdensityinter(atmnet[, , 3], lftm)

desmat[1, 1 + 6] <- fdensity(rtnet[, , 1])
desmat[1, 2 + 6] <- fdensity(rtnet[, , 2])
desmat[1, 3 + 6] <- fdensity(rtnet[, , 3])
desmat[2, 1 + 6] <- fdensityintra(rtnet[, , 1], vrouwm)
desmat[2, 2 + 6] <- fdensityintra(rtnet[, , 2], vrouwm)
desmat[2, 3 + 6] <- fdensityintra(rtnet[, , 3], vrouwm)
desmat[3, 1 + 6] <- fdensityinter(rtnet[, , 1], vrouwm)
desmat[3, 2 + 6] <- fdensityinter(rtnet[, , 2], vrouwm)
desmat[3, 3 + 6] <- fdensityinter(rtnet[, , 3], vrouwm)
desmat[4, 1 + 6] <- fdensityintra(rtnet[, , 1], partijm)
desmat[4, 2 + 6] <- fdensityintra(rtnet[, , 2], partijm)
desmat[4, 3 + 6] <- fdensityintra(rtnet[, , 3], partijm)
desmat[5, 1 + 6] <- fdensityinter(rtnet[, , 1], partijm)
desmat[5, 2 + 6] <- fdensityinter(rtnet[, , 2], partijm)
desmat[5, 3 + 6] <- fdensityinter(rtnet[, , 3], partijm)
desmat[6, 1 + 6] <- fdensityintra(rtnet[, , 1], ethminzm)
desmat[6, 2 + 6] <- fdensityintra(rtnet[, , 2], ethminzm)
desmat[6, 3 + 6] <- fdensityintra(rtnet[, , 3], ethminzm)
desmat[7, 1 + 6] <- fdensityinter(rtnet[, , 1], ethminzm)
desmat[7, 2 + 6] <- fdensityinter(rtnet[, , 2], ethminzm)
desmat[7, 3 + 6] <- fdensityinter(rtnet[, , 3], ethminzm)
desmat[8, 1 + 6] <- fdensityinter(rtnet[, , 1], minoritym)
desmat[8, 2 + 6] <- fdensityinter(rtnet[, , 2], minoritym)
desmat[8, 3 + 6] <- fdensityinter(rtnet[, , 3], minoritym)
desmat[9, 1 + 6] <- fdensityintra(rtnet[, , 1], lftm)
desmat[9, 2 + 6] <- fdensityintra(rtnet[, , 2], lftm)
desmat[9, 3 + 6] <- fdensityintra(rtnet[, , 3], lftm)
desmat[10, 1 + 6] <- fdensityinter(rtnet[, , 1], lftm)
desmat[10, 2 + 6] <- fdensityinter(rtnet[, , 2], lftm)
desmat[10, 3 + 6] <- fdensityinter(rtnet[, , 3], lftm)

colnames(desmat) <- c("friends w1", "friends w2", "friends w3", "atmentions w1", "atmentions w2", "atmentions w3", 
    "retweets w1", "retweets w2", "retweets w3")
rownames(desmat) <- c("total", "same sex", "different sex", "same party", "different party", "same ethnicity", 
    "different ethnicity", "both minority", "same age (<6)", "different age (>5)")
desmat
```

```{r, eval=FALSE}

myeff <- getEffects(mydata)
myeff
```
```{r, eval=FALSE}
#Name is de afhankelijke variabele 
myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "partij", name = "rtnet")

#To answer the second research question, I would like to include different effects. To study the segregation of sex, I think I can still use the sameX effect (to see whether individuals of the same sex are more inclined to retweet one another). 
myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "vrouw", name = "rtnet")
#To answer the second subquestion of the second RQ, we have to see if there is segregation based on age. I believe that during the class we talked about that you just want the normal variable of age (lft), but I don't totally understand why it's not possible to take the variable same age. Let's try lft first. 
myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "lft", name = "rtnet")
#Does afstand just work like this?
myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "afstand", name = "rtnet")
#No it doesn't so I checked the effect in the effectsdocumentation. Here I see that sameX cannot be used for the variable afstand. I'm not sure which of the other effects is useful, I checked them in the Rsiena manual. Maybe incoming shared WWX, but on the other hand I'm not sure if that really tells something about segregation. Let's try reciprocity and then if there's no reciprocity that's segregation (not really but ok)
myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, XRecip, interaction1 = "afstand", name = "rtnet")

myeff_m1 <- myeff
myeff_m1 <- includeEffects(myeff_m1, transTrip, transTies, name = "rtnet")

```
```{r, eval=FALSE}
# I used a seed so you will probably see the same results
myalgorithm <- sienaAlgorithmCreate(projname = "test", seed = 345654)
```
```{r, eval=FALSE}
# to speed things up a bit, I am using more cores.
ansM1 <- siena07(myalgorithm, data = mydata, effects = myeff_m1, useCluster = TRUE, nbrNodes = 2, initC = TRUE, 
    batch = TRUE)
ansM1b <- siena07(myalgorithm, data = mydata, prevAns = ansM1, effects = myeff_m1, useCluster = TRUE, 
    nbrNodes = 2, initC = TRUE, batch = TRUE)
ansM1c <- siena07(myalgorithm, data = mydata, prevAns = ansM1b, effects = myeff_m1, useCluster = TRUE, 
    nbrNodes = 2, initC = TRUE, batch = TRUE)
ansM1d <- siena07(myalgorithm, data = mydata, prevAns = ansM1c, effects = myeff_m1, useCluster = TRUE, 
    nbrNodes = 2, initC = TRUE, batch = TRUE)
```


```{r, eval=FALSE}
save(ansM1, file = "ansM1a.RData")
save(ansM1b, file = "ansM1b.RData")
save(ansM1c, file = "ansM1c.RData")
save(ansM1d, file="ansM1d.RData")
```


```{r, echo=FALSE}
load("/Users/anuschka/Documents/labjournal/data/ansM1a.RData")
load("/Users/anuschka/Documents/labjournal/data/ansM1b.RData")
load("/Users/anuschka/Documents/labjournal/data/ansM1c.Rdata")
load("/Users/anuschka/Documents/labjournal/data/ansM1d.Rdata")
```

```{r}
summary(ansM1)
summary(ansM1b)
summary(ansM1c)
summary(ansM1d)

```

I think we can conclude that there is a negative and weak effect of same gender on retweeting, which means that individuals do not necessarily prefer to retweet someone of the same gender compared to someone of the other gender. Now we have to check how this is the case for individuals of the same age. In the second model I ran, we see that also for same age there is a negative and quite weak effect (-0.0085), so politicians do not prefer to retweet something tweeted by someone of the same age. In sum, the segregation of party affiliation in the retweet network does not seem to be the result of segregation along age and sex. 

<br>

```{r}
summary(ansM1b)
```

Let's continue to test the third RQ. 
I think that to test propinquity, we have to see how close the party members are seated next to each other. This has to do with the variable seats. In the keyf we see the coordinates, but when we study the mydata list, we see that the distance between members is already calculated as a dynamic covariate (afstand). This is what we want to use to test the propinquity. 

```{r, eval=FALSE}
summary(seats)
summary(mydata$dycCovars)
```

<br>

In the output of afstand x reciprocity we see that there is a negative effect (-0.0999) of afstand x reciprocity. I think this means that individuals do not prefer to have a reciprocal relation with someone who is close to them, while the general effect of reciprocity is positive. However, I'm not sure how afstand is now analyzed and whether this effect regards individuals of a lower distance as more of the same. But I also don't know which variable could give a better answer to the research question. 

```{r}

summary(ansM1c)
summary(ansM1d)
```

<br>

To give an answer to the last research question, I believe I do not need to estimate a new model. When we look at the outdegree, we see that this is negative. The only interpretation I wrote down from last week is that that means that individuals want outdegrees but not with everyone in the network. We also see that individuals prefer to have a reciprocal tie rather than a non-reciprocal tie. Politicians thus prefer to retweet someone who also retweets them, rather than retweeting individuals that have not retweeted them. When estimating a model with details about transitivity, we see that there is both a positive effect of transitive triplets as well as transitive ties. Does this then mean that 2 individuals that retweet me also retweet each other? When summarizing these effects, we see that politicians prefer to retweet individuals with whom they already have some kind of connection (through transitivity or to establish a reciprocal relation). Therefore, I think one could conclude that there are structural factors in the network that could link with segregation. However, it is still possible that these structural factors are mostly visible because there already is segregation based on party affiliation. (How can you distinguish what is cause and what is influence?)










